---
title: "AIBL_Dataset Analysis"
author: "Anonymous"
output: html_document
---

```{r}
library(readr)
aibl_apoeres_01_Jun_2018 <-read.csv("C:/Users/newuser.LAPTOP-JVLU65UC/Desktop/Freelance/aibl_apoeres_01-Jun-2018.csv")
aibl_cdr_01_Jun_2018<- read.csv("C:/Users/newuser.LAPTOP-JVLU65UC/Desktop/Freelance/aibl_cdr_01-Jun-2018.csv")
aibl_labdata_01_Jun_2018<-read.csv("C:/Users/newuser.LAPTOP-JVLU65UC/Desktop/Freelance/aibl_labdata_01-Jun-2018.csv")
aibl_medhist_01_Jun_2018<-read.csv("C:/Users/newuser.LAPTOP-JVLU65UC/Desktop/Freelance/aibl_medhist_01-Jun-2018.csv")
aibl_mmse_01_Jun_2018<- read.csv("C:/Users/newuser.LAPTOP-JVLU65UC/Desktop/Freelance/aibl_mmse_01-Jun-2018.csv")
aibl_neurobat_01_Jun_2018<-read.csv("C:/Users/newuser.LAPTOP-JVLU65UC/Desktop/Freelance/aibl_neurobat_01-Jun-2018.csv")
aibl_ptdemog_01_Jun_2018<-read.csv("C:/Users/newuser.LAPTOP-JVLU65UC/Desktop/Freelance/aibl_ptdemog_01-Jun-2018.csv")
aibl_pdxconv_01_Jun_2018<-read.csv("C:/Users/newuser.LAPTOP-JVLU65UC/Desktop/Freelance/aibl_pdxconv_01-Jun-2018.csv")

#Merge the data
library(tidyverse)
df_list<- list(aibl_apoeres_01_Jun_2018,aibl_cdr_01_Jun_2018,aibl_labdata_01_Jun_2018,aibl_medhist_01_Jun_2018,aibl_mmse_01_Jun_2018,aibl_neurobat_01_Jun_2018,aibl_ptdemog_01_Jun_2018,aibl_pdxconv_01_Jun_2018)
total<-df_list %>% reduce(inner_join,by='RID')
dim(total)
summary(total)
glimpse(total)
str(total)

#Replacing both MCI and AD label as 2 in the target variable
total$DXCURREN[total$DXCURREN == 3]<-2
total$DXCURREN[total$DXCURREN == 7]<-2
total$DXCURREN[total$DXCURREN ==-4]<-2
library(dplyr)
table(total['DXCURREN'])
total %>%
  count(DXCURREN)
#Typecasting date type columns
total$EXAMDATE<-as.Date(total$EXAMDATE,'%m/%d/%Y')
total$EXAMDATE.x<-as.Date(total$EXAMDATE.x,'%m/%d/%Y')
total$EXAMDATE.y<-as.Date(total$EXAMDATE.y,'%m/%d/%Y')

#Missing values
sum(is.na(total))
newdata<-na.omit(total)

#Removing all duplicates
newdata<-distinct(newdata)
dim(newdata)
#Checking categorical string columns
str(newdata)
table(newdata['VISCODE.x'])

table(newdata['VISCODE.y'])
table(newdata['VISCODE.x.x'])
table(newdata['VISCODE.x.x.x.x'])
table(newdata['VISCODE.y.y.y.y'])
table(newdata['PTDOB'])
table(newdata['APTESTDT'])

#More cleansing of data
newdata$APTESTDT<- as.Date(newdata$APTESTDT, '%m/%d/%Y')
newdata$PTDOB<- gsub("/","", as.character(newdata$PTDOB))
newdata$PTDOB<- as.integer(newdata$PTDOB)

#Removing character data with 0 variance
newdata<- subset(newdata, select=-c(VISCODE.x,VISCODE.x.x.x.x,VISCODE.x.x.x,VISCODE.y.y))
dim(newdata)

#Encoding categorical data
str(newdata)
newdata$VISCODE.y<- factor(newdata$VISCODE.y, levels=c('bl','m18','m36','m54','m72'),labels=c(1,2,3,4,5))
newdata$VISCODE.x.x<- factor(newdata$VISCODE.x.x, levels=c('bl','m18','m36','m54','m72'),labels=c(1,2,3,4,5))
newdata$VISCODE.y.y.y.y<- factor(newdata$VISCODE.y.y.y.y, levels=c('bl','m18','m36','m54','m72'),labels=c(1,2,3,4,5))
newdata$VISCODE.y.y.y<- factor(newdata$VISCODE.y.y.y, levels=c('bl','m18','m36','m54','m72'),labels=c(1,2,3,4,5))
str(newdata)

#Converting factor to numeric data type
newdata$VISCODE.y<-as.numeric(newdata$VISCODE.y)
newdata$VISCODE.x.x<-as.numeric(newdata$VISCODE.x.x)
newdata$VISCODE.y.y.y.y<-as.numeric(newdata$VISCODE.y.y.y.y)
newdata$VISCODE.y.y.y<-as.numeric(newdata$VISCODE.y.y.y)
str(newdata)
#Correlation Analysis
nwd<-subset(newdata, select=-c(APTESTDT,EXAMDATE.x,EXAMDATE.y,EXAMDATE))
str(nwd)
dim(nwd)
library(corrplot)
library(RColorBrewer)
source("http://www.sthda.com/upload/rquery_cormat.r")
mdata<-nwd[,c(3,4,7,10,11,12,13,14,15,16,17,18,19,20,21,34,37,38,40,44)]
require("corrplot")
rquery.cormat(mdata)

rquery.cormat(mdata, type="full")

```

Comments: The correlation plot shows the correlation among the chosen variables. As we can see from the graph, the multicollinearity problem is not high among the variables

```{r}
library(DataExplorer)
#Removing the RID, SITEID
nw<- select(nwd, -RID,-SITEID.x,-SITEID.y,-SITEID.x.x,-SITEID.y.y,-SITEID.x.x.x,-SITEID.y.y.y,-SITEID.x.x.x.x,-SITEID.y.y.y.y)

head(nw)
str(nw)

#Visualizations
plot_str(nw)
plot_bar(nw)
plot_bar(nw,by="DXCURREN")
plot_boxplot(nw,by="DXCURREN")
plot_correlation(nw)

```

Comments: The plotted bar graph, stacked bar with respect to binary target variable , boxlot w.r.t to target variable and correlation plot has been shown.

```{r}

#Typecasting target variable as factor
typeof(nw$DXCURREN)
nw$DXCURREN<-as.factor(nw$DXCURREN)

#Blood analysis density plot with respect to Diagnosis

library(caret)
library(lattice)
xyplot(DXCURREN~HMT3,data=nw)
xyplot(DXCURREN~AXT117,data=nw)
xyplot(DXCURREN~RCT6,data=nw)
```

Comments: The scatter plot has shown the density distribution of red blood cells,thyroid stim. hormone and urea nitrogen with respect to diagnosis.

```{r}
#Density plot of blood analysis
dens <- density(nw$RCT20)
plot(dens,col='steelblue',main="Density plot of RCT20")

dens1 <- density(nw$RCT11)
plot(dens1,col='steelblue',main="Density plot of RCT11")

dens2<-density(nw$BAT126)
plot(dens2,col='steelblue',main="Density plot of BAT126")
```
Comments:The density distribution cholestrol,serum glucose and vitamin B12

```{r}
str(nw)
#Removing unnecessary variables
nw <- subset(nw,select=-c(VISCODE.y,VISCODE.x.x,VISCODE.y.y.y,VISCODE.y.y.y.y,PTDOB))
dim(nw)
str(nw)
#Imbalanced data check
prop.table(table(nw$DXCURREN))
```
Comments: Data distribution of the target variable class. Data is imbalanced.

```{r}
#Validation for preprocessing
#Logistic regression model
set.seed(100)
library(caTools)
spl<-sample.split(nw$DXCURREN,SplitRatio=0.7)
train<-subset(nw,spl==TRUE)
test<- subset(nw,spl==FALSE)
dim(train)
dim(test)
model_glm <-glm(DXCURREN~ . ,family='binomial',data=train)
summary(model_glm)
#predictions 
predictTrain <- predict(model_glm,data=train,type="response")
#confusion matrix
table(train$DXCURREN,predictTrain>=0.5)
(189414+40325)/nrow(train)
#Predictions on test set
predictTest= predict(model_glm,newdata=test,type="response")
#Confusion matrix
table(test$DXCURREN, predictTest>=0.5)
(81224+17299)/nrow(test)

```
Comments: Our preprocessing has been quite well , as both test and train data have given around 92% accuracy.
